---
title: "Problem Set 4"
author: "Simone Chu"
date: "2/25/2019"
output: html_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(janitor)
library(knitr)
library(gt)
```

```{r madlibs, include=FALSE, message=FALSE, echo=FALSE}
nc_09 <- read_csv("ps_4_elections-poll-nc09-3.csv") %>%
  filter(!is.na(file_race),
         !is.na(response),
         !is.na(ager == "[DO NOT READ] Refused"),
         !is.na(final_weight),
         educ != "[DO NOT READ] Refused") 

n_dem_support <- nc_09 %>%
  filter(response == "Dem") %>%
  count()
  
only_reps <- nc_09 %>%
    filter(response == "Rep") %>%
    count()

only_und <- nc_09 %>%
  filter(response == "Und") %>%
  count()

rep_vs_und <- (only_reps) - (only_und) 

gender_compare <- nc_09 %>%
  select(gender, gender_combined) %>%
  filter(gender != gender_combined) %>%
  count()
  
race_eth_v_file_race <- nc_09 %>%
  filter(race_eth == "White") %>%
  filter(file_race_black != "White") %>%
  count()

1st_rep_response <- nc_09 %>%
  
```
### Question 1

There were `r n_dem_support` respondents who supported the Democratic candidate. 

There were `r rep_vs_und` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (`gender` and `gender_combined`). There are `r gender_compare` individuals for whom these variables have different values.

There are `r race_eth_v_file_race` respondents listed as “White” under `race_eth` who are not listed as “White” under `file_race_black`.

The first response of Rep came X minutes (rounded to the nearest minute) before the first response of Dem.

### Question 2
```{r chart, include=FALSE, echo=FALSE, message=FALSE}
nc_09 %>%
  filter(race_eth == file_race) %>%
  filter(response == c("Und", "Rep", "Dem")) %>%
  group_by(race_eth) %>%
  select(race_eth, response)
  #gt() %>%
   # tab_header(title = "Voter Preferences by Race") %>%
    #cols_label(race_eth = "Race",
    #  response = "Party")
```

### Question 3



### Collaborators

Margaret Sun, Igor Morzan